HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-16 paper/main.tex
ondrej's comments and fixes

\XXX{Could someone review this for Ondrej:}
Note that for non-configurational languages, the relationship between the
governing and the dependent units is often expressed using morphological
properties of the dependents instead of their ordering (this holds especially for the verb and its
modifiers, less so for components of noun phrases). Since errors in morphology
should be expressed using the traffic lights on the dependent nodes, we would expect
a higher proportion of ``Adequate'' structural units for Czech and Polish.

@@

For example, consider the sentence ``After graduation, Tom moved
to NYC'' \figref{fig:ucca_example}. The atomic units are the individual words,
nodes \#1--6 and the structural nodes are \#7--10. Assume that the translation
is ``After Tom will move to Paris, graduation''\footnote{We take $t$ to
  be in English for presentation purposes. In our experiments $t$ is in German,
  Czech, Polish or Romanian.}.
Then ``after'', ``graduation'', ``Tom'' and ``to'' are marked Green, ``moved'' is marked
Orange (as it corresponds to ``will move'' in $t$), and ``NYC''
is marked as Red, as it was mistranslated to ``Paris''. Node \#9 is marked Adequate,
as the Scene of Tom moving is properly reflected in the translation. Node \#10, which
expresses the relation between the graduation and moving Scenes, is marked Bad,
as their relation in $t$ is reversed.

>>>>

\XXX{Could someone review this for Ondrej:}
Note that for non-configurational languages, the relationship between the
governing and the dependent units is often expressed using morphological
properties of the dependents instead of their ordering (this holds especially for the verb and its
modifiers, less so for components of noun phrases). Since errors in morphology
should be expressed using the traffic lights on the dependent nodes, we would expect
a higher proportion of ``Adequate'' structural units for Czech and Polish
compared to German and Romanian.

@@

For example, consider the sentence ``After graduation, Tom moved
to NYC'' as the source $s$, see \figref{fig:ucca_example}. The atomic units are the individual words,
nodes \#1--6 and the structural nodes are \#7--10. Assume that the translation
$t$
is ``After Tom will move to Paris, graduation''\footnote{We take $t$ to
  be in English for presentation purposes. In our experiments, $t$ is in German,
  Czech, Polish or Romanian.}.
Then ``after'', ``graduation'', ``Tom'' and ``to'' are marked Green, ``moved'' is marked
Orange (as it corresponds to ``will move'' in $t$), and ``NYC''
is marked as Red, as it was mistranslated to ``Paris''. Node \#9 is marked Adequate,
as the Scene of Tom moving is properly reflected in the translation. Node \#10, which
expresses the relation between the graduation and moving Scenes, is marked Bad,
as their relation in $t$ is reversed.
